---
title: "ESM 244 Lab 6"
author: "Tom Paschos"
date: "2/13/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Goals:
- read in spatial data
- simplify polygons
- add and transform projections (st_transform, st_cars)
- create a bunch of maps
- join spatial data
- find intersections of spatial data
- interactive plots
- create sf from lat/long coordinates


```{r Load_Packages_Data}

library(tidyverse)
library(sf)
library(tmap)
library(leaflet)
library(ggrepel)
library(ggspatial)
library(RColorBrewer)
library(raster)

```

### Example 1. Dams in California

```{r}

ca_eco <- read_sf(".", layer = "ca_eco") %>% 
  dplyr::select(US_L3NAME) %>% 
  rename(Region = US_L3NAME) %>% 
  st_simplify(dTolerance = 100) %>% 
  st_transform(crs = 4326)


#t_simplify goes through a polygon and says if points are within x distance between nodes it will collapse those onto a single line

```

```{r}

ca_counties <- read_sf(".", layer = "california_county_shape_file")

st_crs(ca_counties) = 4326

```

```{r}

ca_dams <- read_sf(".", layer = "California_Jurisdictional_Dams") %>% 
  rename(Condition = Condition_)

ca_dams$Condition <- fct_relevel(ca_dams$Condition, "Fair", "Satisfactory", "Unsatisfactory", "Poor")

```

MAPS!!! 

```{r}

plot(ca_eco)
plot(ca_counties)

```

Make a map with ggplot

```{r}

color_count <- 13

my_colors <- colorRampPalette(brewer.pal(10, "Set2"))(color_count)

ggplot(ca_eco) +
  geom_sf(aes(fill = Region),
          color = "NA") +
  scale_fill_manual(values = my_colors) +
  geom_sf(data = ca_counties, 
          fill = "NA",
          color = "grey30",
          size = 0.1) +
  geom_point(data = ca_dams,
             aes(x = Longitude, y = Latitude),
             size = 0.75,
             color = "gray10",
             alpha = 0.5) +
  theme_minimal() +
  coord_sf(datum = NA)


# if you wanted to remove the legend: show.legend = FALSE

```

### Example 2. Dams in the Sierra Nevada eco-region

```{r}

# Join info from eco-region with data from dams (only dams with geometries within this sub-region)

sn <- ca_eco %>% 
  filter(Region == "Sierra Nevada") %>% 
  st_join(ca_dams)

ggplot(sn) +
  geom_sf(data = ca_counties, fill = "wheat3", color = "NA") +
  geom_sf(fill = "lemonchiffon4", color = "NA") +
  geom_point(aes(x = Longitude, y = Latitude),
             size = 0.5,
             color = "red4")


```

### Example 3. Eco-regions for Santa Barbara County

```{r}

sb <- ca_counties %>% 
  filter(NAME == "Santa Barbara")

eco_clip <- st_intersection(ca_eco, sb) # clips ca_eco polygon by the bounds of the sb polygon

ggplot(eco_clip) +
  geom_sf(data = ca_counties, 
          fill = "gray90", 
          color = "gray80", 
          size = 0.2) +
  geom_sf(aes(fill = Region), color = "NA") +
  scale_fill_manual(values = c("darkolivegreen2","darkolivegreen","gold2")) +
  coord_sf(xlim = c(-121, -119), ylim = c(33.5, 35.5)) +
  geom_point(aes(x = -119.6982, y = 34.4208), size = 2) +
  geom_text (x = -119.6982, y = 34.35, label = "Santa Barbara") +
  theme_minimal() +
  theme(legend.position = c(0.5, 0.15)) +
  labs(x = "Longitude", y = "Latitude")




```

### Example 4. Intro to Interactive Plots with tmap

```{r}

map_sb_eco <- tm_shape(eco_clip) +
  tm_fill("Region", palette = "RdPu", alpha = 0.5) +
  tm_shape(ca_counties) +
  tm_borders()

tmap_mode("view") # this makes the map interactive
map_sb_eco

# Example with a different basemap - type in leaflet::providers in the console to see a list

```

### Example 5. Fault Lines

```{r}

fault_lines <- read_sf(".", layer = "GMC_str_arc") %>% 
  st_transform(crs = 4326) %>% 
  separate(LTYPE, into = c("syn_ant", "certainty", "direction"), sep = ",")

plot(fault_lines)

ggplot() +
  geom_sf(data = ca_counties, fill = "black", color = "NA") +
  geom_sf(data = fault_lines, aes(color = syn_ant)) +
  theme_minimal()

# Fault lines in SB County

sb_faults <- fault_lines %>% 
  st_intersection(sb)

ggplot() +
  geom_sf(data = sb) +
  geom_sf(data = sb_faults, aes(color = syn_ant))

tm_basemap("CartoDB.DarkMatter") +
  tm_shape(sb) +
  tm_borders(col = "gray50", lwd = 2) +
  tm_shape(sb_faults) +
  tm_lines(col = "syn_ant", palette = c("orange", "purple"), lwd =2)

```

### Example 6. Faceted maps

```{r}

ggplot() +
  geom_sf(data = ca_counties, fill = "black", color = "NA") +
  geom_sf(data = fault_lines, aes(color = syn_ant)) +
  facet_wrap(~syn_ant)

```

### Example 7. Making spatial points

```{r}

ca_sites <- read_csv("cadfw_sensitive_sites.csv")

sites_sf <- st_as_sf(ca_sites, coords = c("LONDD", "LATDD"), crs = 4326) # makes these sticky geometries

ggplot() + 
  geom_sf(data =  ca_counties, fill = "gray40") +
  geom_sf(data = sites_sf, aes(color = PRI_CODE), size = 0.3)

```

### Example 8. Chloropleth of CA counties by NUMBER of dams in each county

```{r}

intersection <- st_intersection(ca_dams, ca_counties)

dams_per_county <- intersection %>% 
  group_by(NAME) %>% 
  tally()

ca_tot <- ca_counties %>% 
  st_join(dams_per_county) %>% 
  dplyr::select(NAME.x, n) %>% 
  rename(name = NAME.x)

# Reassign NA values to zero:

ca_tot$n[is.na(ca_tot$n)] <- 0

ggplot() +
  geom_sf(data =ca_tot, aes(fill = n), size = 0.2) +
  theme_minimal() +
  scale_fill_continuous(low = "yellow", high = "red")

```

